%-------------------------
% Resume in Latex
% Author : Jordan Addison
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://mscoast.dev/}{\Large Jordan Addison}} & Email : \href{mailto:jordanrileyaddison@gmail.com}{jordanrileyaddison@gmail.com}\\
  \href{https://mscoast.dev/}{https://mscoast.dev} & Mobile : +1-228-547-0060 \\
\end{tabular*}

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
    \textbf{Proficient with}{: Javascript, Typescript, NodeJS, GraqhQL, Redux, React, C\#, SQL, HTML, CSS, NGINX, Browser accessibility best practices}
   }
   \item{
    \textbf{Familiar with}{: RabbitMQ, Jenkins, Redis}
  }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Global Financial Aid Services}{Gulfport, MS}
      {Senior Software Engineer}{Oct 2015 - Present}
      \resumeItemListStart
        \resumeItem{Datacheck}
          {Led technical direction on greenfield SaaS application that allowed school administrators to access data from the National Student Loan Data System allowing them to quickly verify previous loans and eligibility for new loans.}
        \resumeItem{SAINT Student}
          {Modernized Legacy Website with 2000+ HTML pages to use a modern build system (Gulp). Using Javascript, CSS and the Pug templating engine allowed for common markup and code sharing. Built custom AST transforms to preserve legacy interpolation in the pug templates. Followed ARIA best practices to provide an consistent and cohesive experience for disabled users and to allow for Section 508 AA compliance. Integrated login and authentication flows into modern login system allowing for 2 factor authentication, user self service and more fine grained branding controls for our clients custom student login portals.}
        \resumeItem{GlobalCORE}
          {Integrated 2 factor authentication into legacy ASP.NET web application. Modernized Windows administration application to web application using Next.js allowed for migration from legacy application through modern login system.}
        \resumeItem{Global Authentication}
          {Implemented Custom Identity Server 4 paired with ASP.NET Identity for a multi tenant authentication and authorization system to power multiple products.}
        \resumeItem{Global Email API}
          {Designed and built custom email API in Node.JS allowing for a cohesive branding between products. Api writes to a RabbitMQ message bus and a worker process picks up the jobs and actually sends the emails to keep things smooth and fast.}
        \resumeItem{Global SMS API}
          {Designed and built custom SMS API in Node.JS, integrates with twilio and keeps track of opt outs to provide custom messaging in User interfaces accross multiple products.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd
% --------Multiple Positions Heading------------
    \resumeSubSubheading
    {Software Engineer / Software Configuration Manager}{Oct 2013 - Sep 2015}
    \resumeItemListStart
      \resumeItem{QA Environment}
        {Streamlined QA environment used by 10+ QA Testers}
      \resumeItem{QA Student Creation}
        {Built tools to bring a 5-10 minute manual process down to 10 seconds saving testers hours per week creating test cases.}
      \resumeItem{Build System}
        {Upgraded legacy build system to Jenkins providing more modern build features and faster builds for 50+ internal and external products}
    \resumeItemListEnd
    \resumeSubSubheading
    {QA Analyst}{Oct 2012 - Sep 2013}
    \resumeItemListStart
      \resumeItem{Testing}
        {Followed testing best practices to ensure our products worked as intended.}
    \resumeItemListEnd
%-------------------------------------------

\end{document}